Cyclone: High Availability for Persistent Key Value Stores

### 2017-12-21 paper/paper.tex
Update.

\section{Network}
\label{sec:network}
Cyclone uses the RAFT~\cite{raft} consensus protocol to replicate the
log of operations across machines. The key bottleneck in log
replication in Figure~\ref{fig:problem} is the CPU - the achieved
network throughput at load is well under the capacity of the 10 Gbps
link.  The key to improving CPU utilization for log replication is the
insight that log replcation protocols such as RAFT are oblivious to
the actual contents of the log entry being replicated.  This
observation allowed us to greatly improve replication performance by
building a (near) zero copy implementation of RAFT. Cyclone's
implementation of RAFT does only a small \emph{constant} amount of
work per replicated log entry on the CPU leaving the (commodity) NIC
to do the rest of the heavy lifting.

>>>>

\section{Network}
\label{sec:network}
Cyclone uses the RAFT~\cite{raft} consensus protocol to replicate the
log of operations across machines. The bottleneck for log replication
in Figure~\ref{fig:problem} is the CPU - the achieved network
throughput at load is well under the capacity of the 10 Gbps link. The
key to improving CPU utilization for log replication is the insight
that log replcation protocols such as RAFT are oblivious to the actual
contents of the log entry being replicated.  This observation allowed
us to greatly improve replication performance by building a (near)
zero copy implementation of RAFT. Cyclone's implementation of RAFT
does only a small \emph{constant} amount of work per replicated log
entry on the CPU to run the RAFT protocol state machine.  Copying work
that proportional to the amount of data being replicated is done by
the (commodity) NIC.  We therefore shift the bottleneck to the NIC,
making full use of the available network link.
